This thesis aimed to create a~prototype of the~server part of a~role-playing game with features of augmented reality. I explored and analyzed similar existing games. After discussion with my colleague Tomáš Zahálka, I defined the~rules and features of the~game prototype. 

I analyzed use cases and specified requirements to clarify expected server behavior. I explored available solutions for a~\textit{database management system} and chose to use \textit{MySQL}. I incorporated several Java frameworks and libraries into the~project to handle database communication, JSON (de)serialization, and to manage API endpoints. I designed the~structure of the~server and described actions a~user can perform. Based on these actions, I created a~specification for public API as well as private one for internal communication among components. I designed and implemented a~database model. I obtained and imported initial game locations to the~database. In implementation phase, I created all specified API endpoints, implemented game logic, and database communication. Administration section was secured and requires authentication. I created an index of location and configured a~cache to improve database performance. Lastly I performed unit, system  and stress tests as well as static code analysis.

Since the~server is currently in prototype version, many features and further improvements are planed for future development. I plan to improve error handling and increase coverage of the~unit tests before a~production release. One of the~planned features is a~quest system. My design allows easy scalability to support many concurrent users and high extensibility which enables me to create full, market-ready server.