\section{Goals of the~Thesis}
The thesis is mainly focused on the~practical game server development. In the~research part, I will analyze existing augmented reality games, research available database management systems and explore frameworks commonly used for server development.

In the~practical part, I will specify features and requirements for the~server. The goal is to support actions the~mobile client might need to perform for seamless gaming experience. These operations include for example finding game objects near a~player, or getting user's profile information. The main goal is to implement server's functionality to communicate with clients, parse their requests and respond in valid format. The underlying goals include the~need to use a~database, caching, and to manage communication with external services. Lastly, the~game server prototype should be tested and deployed.	

\section{Game Description}
This is a~role-playing mobile game with augmented reality features. Player becomes a~character in an invisible alternative reality. He can explore the~new, magical world using his phone which displays a~map with objects around him. Player can discover monsters, like goblins or skeletons, and fight them to death for a~reward. As he gains more experience and gold, he can buy himself more powerful weapons and armor in a~shop. Tired of running in the~outside world? Player can exchange his real money for in-game gold.

For prototyping purposes, some described features are limited. All available actions are specified in \textit{Features} section of Requirements \ref{section:fr}.

\section{Game Story}
It was an ordinary Monday morning. Citizens of Flek, a~small city in the~heart of the~civilization, just woke up and poured to the~streets. Abruptly, a~loud cry pierced the~morning noise. 

“Make way! Make way!” yelled a~little boy while quickly elbowing his way through the~crowd, carefully holding a~piece of bread. People muttered silent curses, nevertheless they were moving out of his way to avoid his sharp elbows.

“Thief! Stop him! Stop the~boy!” suddenly echoed from the~other side of the~market square. City guards noticed the~boy had stolen the~bread from a~well-known baker. A hunt began, everyone was trying to take down the~boy. It didn’t take long and he was surrounded by the~guards, pinned down by a~local fat man who accidentally slipped and fell on the~boy. Guards tied him down, “Fiddle, again. We gave you a~warning the~last time. You are going with us.” City of Flek takes stealing very seriously. Poor Fiddle was sentenced to 15 years in prison.

Eight years later, a~boy became a~man. “Open up the~door,” someone said. The creaking door of the~cell slowly opened. A king himself entered. “Down on your knees, Fiddle.” said king. “I heard stories about you. I need someone like you, someone who has nothing to lose. I want you to go on a~quest. If~you succeed, you’ll be free.”

“What quest, Your Highness?” asked Fiddle.

“An old wizard told me, there are dragon eggs somewhere, still alive and ready to be hatched. As you might know, young dragons are easily trained to serve its owner. We are on a~verge of a~war with our neighbors. And they are stronger.” the~king sat down on Fiddle’s bed. “I want you to find those eggs and bring them to us. Dragons are extinct for over a~century. With dragon warriors, we’ll be the~most powerful nation in the~world.”

“I do not want to go on the~quest.” Fiddle looked up.

“Then you’ll be executed tomorrow.” the~king responded

“Ummm, alright then. You leave me no choice. I’ll find those dragon eggs for you.” said defeated Fiddle.

“Good. Take this device. It contains a~map of your surroundings. Now go!”
